---
title: "What is Data Science"
format: html
editor: visual
---

## What is a Data Scientist?

Being a data scientist is about using data to answer important questions and create solutions. It involves programming, statistics, visualization, and domain expertise.

### Similarities and Differences with Statisticians

-   **Similarities**
    -   Both work with data and uncertainty
    -   Both value careful modeling and interpretation
-   **Differences**
    -   Statisticians often focus on theory and inference
    -   Data scientists work more with messy data and machine learning

### My Perspective

I see myself between the two: - I value the rigor of statistics - I enjoy the flexibility and problem-solving in data science

------------------------------------------------------------------------

## R Code Practice

```{r}
y <- density(iris$Petal.Width)
class(y)
typeof(y)
str(y)

```

```{r}
plot(y)
```

The `echo: false` option disables the printing of code (only output is displayed).
